---
title: "CameraTrapDetectoR: User Manual"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{CameraTrapDetectoR: User Manual}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


coming soon!  

## Get Started 

Intro: 

### Package installation
View detailed [installation instructions](https://github.com/CameraTrapDetectoR/CameraTrapDetectoR) on Github.

Load the package:  
```{r load}
library(CameraTrapDetectoR)
```

Notes before first use  

## Using CameraTrapDetectoR  

### CameraTrapDetectoR in R  



### CameraTrapDetectoR in R Shiny  
CameraTrapDetectoR provides a user-friendly interactive application where you can specify input arguments in drop-down format. This allows users with less familiarity in R coding to fluently use this package. To load the application, run the following line of code in your R or RStudio console:  
  
```{r loadShiny, eval=FALSE}
runShiny("deploy")
```  
  
To follow a full example of using the CameraTrapDetectoR Shiny app, check out our [demo](add link here).   

### CameraTrapDetectoR Desktop Package    
The CameraTrapDetectoR Shiny app can be deployed by users without ever accessing R or RStudio.

This option is slower to load than other methods of using CameraTrapDetectoR, and is the preferred option only for users with no R experience.   


## Evaluating Output  


