---
title: "Shiny Demo"
output: 
  rmarkdown::html_vignette:
    toc: true
    self_contained: true
vignette: >
  %\VignetteIndexEntry{Shiny Demo}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
## Before you start  
  
### Who is this for?   
Users who have R or RStudio installed but may be less comfortable with coding.  
Anyone using the CameraTrapDetectoR desktop application. The interface is exactly the same as the Shiny application.  
Anyone who prefers a drop-down menu for setting function arguments.  
Anyone new to using CameraTrapDetectoR can benefit from this detailed example, even those who will be running the function directly in an R Console or script.  

### Organize your image directory  
  
  
## Open the CameraTrapDetectoR Shiny application  

Once you have [installed](https://github.com/CameraTrapDetectoR/CameraTrapDetectoR) CameraTrapDetectoR, copy + paste the following lines of code in your Console:  

```{r setup, eval = FALSE}
library(CameraTrapDetectoR)
runShiny("deploy")
```
  
## Arguments   

## Troubleshooting  

